The ChEMBL database as Linked Open Data

### 2012-05-02 article.tex
First citation is ref. 1
add email address

\usepackage{a4wide}  % Formatting web addresses  
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}
\usepackage[citestyle=numeric-comp]{biblatex}                                                                     
\setlength{\bibitemsep}{0cm}                                                                                                                
\renewbibmacro{in:}{%                                                                                                                       
  \ifentrytype{article}{}{%                                                                                                                 
  \printtext{\bibstring{in}\intitlepunct}}}                                                                                                 
\addbibresource{article.bib}

@@

\author{Egon~L.~Willighagen$^{1}$\email{Egon~L.~Willighagen - egon.willighagen@maastrichtuniversity.nl}\and
Andra~Waagmeester$^1$\email{Andra Waagmeester - FIXME}\and
Ola Spjuth$^2$\email{Ola Spjuth - FIXME}\and
Peter~Ansell$^3$\email{Peter Ansell - FIXME}\and
Antony~Williams$^4$\email{Antony Williams - FIXME}\and
Valery~Tkachenko$^4$\email{Valery Tkachenko - FIXME}\and
Janna~Hastings$^5$\email{Janna Hastings - FIXME}\and
John~Overington$^6$\email{John Overington - FIXME}\and
Anna~Gaulton$^6$\email{Anna Gaulton - FIXME}\and
Mark~Davies$^6$\email{Mark Davies - FIXME}\and
Bin~Chen$^7$\email{Bin Chen - FIXME}\and
David~Wild$^7$\email{David Wild - FIXME}
}

>>>>

\usepackage{a4wide}  % Formatting web addresses  
\usepackage{url}  % Formatting web addresses  
\usepackage{ifthen}  % Conditional 
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}
\usepackage[citestyle=numeric-comp,sorting=none]{biblatex}
\setlength{\bibitemsep}{0cm}                                                                                                                
\renewbibmacro{in:}{%                                                                                                                       
  \ifentrytype{article}{}{%                                                                                                                 
  \printtext{\bibstring{in}\intitlepunct}}}                                                                                                 
\addbibresource{article.bib}

@@

\author{Egon~L.~Willighagen$^{1}$\email{Egon~L.~Willighagen - egon.willighagen@maastrichtuniversity.nl}\and
Andra~Waagmeester$^1$\email{Andra Waagmeester - FIXME}\and
Ola Spjuth$^2$\email{Ola Spjuth - FIXME}\and
Peter~Ansell$^3$\email{Peter Ansell - p\_ansell@yahoo.com}\and
Antony~Williams$^4$\email{Antony Williams - FIXME}\and
Valery~Tkachenko$^4$\email{Valery Tkachenko - FIXME}\and
Janna~Hastings$^5$\email{Janna Hastings - FIXME}\and
John~Overington$^6$\email{John Overington - FIXME}\and
Anna~Gaulton$^6$\email{Anna Gaulton - FIXME}\and
Mark~Davies$^6$\email{Mark Davies - FIXME}\and
Bin~Chen$^7$\email{Bin Chen - FIXME}\and
David~Wild$^7$\email{David Wild - FIXME}
}
